%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------
\usepackage[most]{tcolorbox}
\usepackage{xcolor}

\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=black,
	colframe=white,
	coltext=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
	boxsep=5pt,
    arc=0pt,outer arc=0pt,
    }
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Radu}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Cebotari}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Full-Stack Web Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Iași, România}\\
	\icon{Phone}{12}{+40 740 604 889}\\
	\icon{At}{12}{\href{mailto:ianknote@gmail.com}{ianknote@gmail.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	% \icon{Globe}{12}{\href{https://alyx.vance.me}{alyx.vance.me}}\\
	\icon{Github}{12}{\href{https://github.com/sinnerJoe}{SinnerJoe}}\\
	\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/radu-cebotari-30763a120/}{Radu C.}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	Hey there! I'm a fullstack software engineer passionate about human-software interaction 
	and general software design. I am communicative when I'm not single mindedly 
	focused on solving a problem and constantly looking for improvement 
	in my soft and hard skills departments. I draw pleasure
	from writing good quality code and learning new things from other people. \\
	I'm looking forward to working on challenging problems. If you need somebody
	for building great software - here I am!

\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{JavaScript}{95}
		\baritem{NodeJS}{95}
		\baritem{Angular 6}{65}
		\baritem{React}{95}
		\baritem{HTML}{95}
		\baritem{CSS/SCSS}{88}
		\baritem{SQL}{95}
	\end{barchart}
	
\end{minipage}

\begin{center}
	\bubbles{6/git, 3/Mongo, 6/Confluence, 6/JIRA, 5.2/PostgreSQL}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}

	\entry
		{11/2021 -- present}
		{Full-stack engineer}
		{OysterHR}
		{ Implement the front-end and back-end of the features I develop. 
		\\   \textbf{Some highlights:}
		\begin{itemize}
			\setlength\itemsep{0em}
				\item I rewrote more than 3k lines of JS into TS. 
				\item Developed several user-facing featurs
				\item Became moderately proficient in Ruby on Rails
		\end{itemize}
			\texttt{Typescript}\slashsep
		\texttt{Tailwind CSS}\slashsep
		\texttt{React}\slashsep
		\texttt{Ruby on Rails}
		}

	\entry
		{5/2021 -- 11/2021}
		{Front-end engineer}
		{Amazon}
		{ I developed UIs using different front-end frameworks. Fixed tech debt and maintained old apps that used ancient technologies. Lead the development of the front-end part 
			of the newer projects, was in charge of picking the technologies and developing the architecture of the app. Participated in the on-call rotation.
		\\   \textbf{Some highlights:}
		\begin{itemize}
			\setlength\itemsep{0em}
				\item I upgraded the version of Angular of our project from version 7 to 12 along with other related dependencies.
				\item Developed a project for marking different zones in a screenshot with draggable rectangles that had zoom in/out functionality with touchpad support.
				\item Implemented a WYSIWYG editor using the command pattern and quil.js library.
		\end{itemize}
        \texttt{Angular 12}\slashsep
        \texttt{Angular.js}\slashsep
        \texttt{Rx.js}\slashsep
		\texttt{Typescript}\slashsep
		\texttt{Tailwind CSS}\slashsep
		\texttt{React}\slashsep
		\texttt{Framer Motion}
		}
	
	\entry
		{5/2020 -- 5/2021}
		{Front-end developer}
		{Luxoft}
		{ I developed UI components, screens and fix bugs in the UI of an app for displaying network stats from Cisco equipment and configuring them. 
			I work in direct collaboration with the backend team from India and US management.
		\\   \textbf{Some highlights:}
		\begin{itemize}
			\setlength\itemsep{0em}
				\item Introduced \textit{rc-field-form} and implemented an abstraction layer over it.
				\item Developed a component that renders a customizable table with editable/removable rows with support for validation using the aforementioned form library.
				\item Refactored the whole Redux store (40+ actions) into slices using Redux Toolkit.
		\end{itemize}
        \texttt{React.js}\slashsep
		\texttt{Javascript}\slashsep
		\texttt{SASS}\slashsep
		\texttt{Lodash}\slashsep
		\texttt{Redux Toolkit}
		}
	\entry
		% {1 year}
		{8/2019 -- 5/2020}
		{Full stack developer}
		{Safeguard}
		{I worked on many modules that are part of the Safeguard Global system. I maintaned 
		long SQL queries, developed modules in NodeJS and Go. I refactored big and
		 clunky JS and SQL code into shorter and easier to understand code. 
		\\   \textbf{Some highlights:}
		\begin{itemize}
			\setlength\itemsep{0em}
				\item Developed several reusable higher order components used in dozens of screens. 
				\item Refactored 10 front-end screens using those components. 
				\item Developed a microservice in Golang. 
				\item \href{https://www.npmjs.com/package/react-paginate-next}{\textcolor{blue}{\underline{Forked}}} the popular "react-paginate" component, fixed inconsistencies and optimized it.
				\item Wrote 10+ documentation pages on Confluence.
		\end{itemize}
		\texttt{NodeJS}\slashsep
		\texttt{Koa.js}\slashsep
		\texttt{React}\slashsep
		\texttt{PostgreSQL}\slashsep
		\texttt{Go}\slashsep
		\texttt{RabbitMQ}\slashsep
		\texttt{Bootstrap 3}
		}
	\entry
		{6/2018 -- 4/2019}
		% {8 months}
		{Fullstack Web Developer}
		{Heavensolutions}
		{I worked on a website project started from scratch which goal was connecting trip organisers 
		with tourists. I was implicated in the development of both the front-end(Angular 6) and back-end.
		 We were the first to use the PrivateSky framework developed by the A.I. Cuza university in
		 a real-world software-product. I also wrote several tests for PrivateSky.
		\\  \texttt{node.js}\slashsep
			\texttt{Angular 6}\slashsep
			\texttt{express.js}\slashsep
		    \texttt{PrivateSky}\slashsep
		    \texttt{Sequelize}\slashsep
		    \texttt{Agile}
		}
	% \entry
	% 	{5/2016 -- 7/2016\\\footnotesize{internship}}
	% 	{Java Backend Developer}
	% 	{Esempla}
	% 	{I developed a small Spring MVC project for buying tickets and tracking buses of a bus station.
	% 	 I also developed plugins for the vRealize Orchestrator software.
	% 	\\ \texttt{Java}\slashsep
	% 	   \texttt{Spring MVC}\slashsep
	% 	   \texttt{vRealize Orchestrator}
	% 	   }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2016 -- 2021}
		{Bachelor's Degree in Computer Science}
		{Alexandru Ioan Cuza University, Iași}
		{\texttt{Java}\slashsep
		 \texttt{C++}\slashsep
		 \texttt{Haskell}\slashsep
		 \texttt{Oracle PL/SQL}\slashsep
		 \texttt{Android}\slashsep
		 \texttt{Kotlin}\slashsep
		 \texttt{Scala}
		}
	% \entry
	% 	{2012 -- 2016}
	% 	{High School}
	% 	{Center of Excelence in Infomatics, Chișinău}
	% 	{Along with studying algorithms we were taught MS T-SQL, PHP, Java, C\#, Windows Forms, WPF.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{Romanian} - native\\
	\textbf{Russian} - proficient\\
	\textbf{English} - proficient
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	Running, playing football, coding, psychology
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
